% Put your acknowledgement here

\begin{acknowledgement}

The researcher would like to express his gratitude to the Professional Development assistance that was provided by the \textbf{International School Manila}, which allowed the researcher to be able to undertake this course and conduct this capstone project. The support of the institution reflects its recognition of the importance of continuing learning, professional development and strengthening of systems to support school operations. 

Special thanks to the people inside \textbf{International School Manila}, particularly those in \textbf{Finance} and \textbf{Accounting}, \textbf{Admissions}, \textbf{IT} and \textbf{Student Charging operations}, who provided their process knowledge, participated in consultations and pilot testing of the system. Their practical experience proved to be very valuable in the formulation of the project requirements and keeping the study relevant with the institutional needs. 

The researcher would also like to express heartfelt gratitude to \textbf{Finance Director Joel Songco} for his assistance, encouragement and guidance in the development and pilot validation of this project. His support enabled the project to be placed in the needs of Finance and the overall billing process of the institution. 

The researcher also wishes to thank the adviser, \textbf{Katrina Joy M. Abriol-Santos}, for her insight, patience and constant feedback that guided the direction and rigor of this research. The authors also gratefully acknowledge the support and comments of the IT Developers, the reviewers, administrative staffs, and IS 295 classmates that assisted by providing comments, suggestions, and peer reviews that helped improve the pilot web application deployed and the manuscript. 

Special thanks to \textbf{Paolo Escotido} and \textbf{Jefferson Legaspi}, co-worker and classmates, respectively, of the researcher for the technical and personal assistance given during this course and during the completion of this capstone project. 

Lastly, heartfelt thanks go to the researcher’s \textbf{family} and \textbf{friends} for their patience, understanding, help, and encouragement while this deployed pilot web application and manuscript was completed.
\end{acknowledgement}